---
title: "EDA"
author: "Kristian Maras"
date: "2024-01-18"
output: html_document
---

## Exploration Data Analysis on S18 Sheep

Load libraries and aggregated data
```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
library(here)
library(tidyverse)
library(stringr)
library(skimr)
library(plotly)
library(RColorBrewer)
#just for saving plots
library(reticulate)
use_python("/Users/kris/miniconda3/bin/python")
import("kaleido")
import("plotly")
source("paths.R")
get_paths()

aggregate_data <- list.files(path = generated_data_path, 
            pattern = "NestedDataS[0-9]+\\.rds", 
            full.names = TRUE) %>% map(readRDS) %>% bind_rows()


cleaned_aggregate_data <- readRDS(file = here::here(generated_data_path,"filtered_aggregate_data.rds"))
cleaned_aggregate_long_data <- readRDS(file = here::here(generated_data_path,"cleaned_aggregate_long_data.rds"))
```


```{r}
#Double check generated data is consistent with data dictionary

aggregate_data %>% filter(sheep == "S18") %>% 
  filter(WaveFront == "SR",Catheter_Type == "Penta", Point_Number == 4815) %>%
  select(signal) %>%
  unlist() %>%
  plot(type = "l")

```

Coincidently, the raw data looks like
```{r}

aggregate_data %>% filter(sheep == "S18") %>% 
  filter(WaveFront == "SR",Catheter_Type == "Penta", Point_Number == 4815) %>%
  select(rawsignal) %>%
  unlist() %>%
  plot(type = "l")

```

High level split of count of observations with and without histology info. Note - The histology data is sometimes blank and a signal is sometimes not present. Generally
the number of observations that have histology labels (0 or 1) are outnumber by those that dont, particularly with S20.

```{r paged.print=FALSE}
aggregate_data %>% group_by(sheep,Catheter_Type,WaveFront) %>% 
  summarise(histology_count = sum(!is.na(endocardium_scar)),
            no_histology_count = sum(is.na(endocardium_scar))) %>% 
  arrange(sheep,desc(histology_count))

```

Looking at cleaned data only, some sheep (s20 SR wavelenth) have more imbalanced scar v no scar labels

```{r}


cleaned_aggregate_data %>% filter(!is.null(signal)) %>%
  filter(!is.na(endocardium_scar)) %>% 
  group_by(sheep,Catheter_Type,WaveFront, Categorical_Label) %>% 
    summarise(count = n())
  
  


```

The available data reduces as not all data points have signal info along 
with not all points having histology info (blanks in cleaned_histology_all file).

We feed both the filtered (blanks in cleaned_histology_all and no signal) and imputed (blanks are treated as zeros in labells) to the orange data mining analysis.

The proportion of Scar and NoScar "roughly" balanced.

```{r}
aggregate_data %>% filter(!is.null(signal)) %>% count(Categorical_Label)

```


Notably, even though the S20 sheep is the control subject, it still has a significan portion of scar (2K) versus no-scar (3.6K). See below:
```{r}
aggregate_data %>% filter(!is.null(signal)) %>% group_by(sheep) %>% count(Categorical_Label)


```

Same thing but by group
```{r}

aggregate_data %>% filter(!is.null(signal)) %>% group_by(sheep,Catheter_Type,WaveFront) %>% 
  count(Categorical_Label)


```

 
 
 
Distribution of signal length assuming there is a signal. Reflects manual calibration 
of starting point for window of interest.
```{r}

summary_window_length <- aggregate_data %>% 
  mutate(length_window = To - From) %>% filter(length_window != 0) %>% 
  group_by(WaveFront, Categorical_Label) %>% select(length_window) 
  

summary_window_length %>%
  plot_ly(x = ~length_window, type = "histogram") %>%
  layout(barmode = "overlay", 
         xaxis = list(title = "Window of interest lenth"),
         yaxis = list(title = "Frequency"),
         title = "Histogram of Distinct Windows of Interest",
         facet_row = ~WaveFront,
         facet_col = ~Categorical_Label)
```

Shows distinct windows of interest by sheep.

```{r}

 aggregate_data %>% filter(!is.na(Categorical_Label)) %>% 
   mutate(length_window = To - From) %>% group_by(sheep) %>% filter(length_window != 0) %>% 
  summarise(mean_window = mean(length_window,na.rm = T))

```
```{r}
save_plot <- function(name,p){
  # Save the plot to a PDF file
  path <- here::here(file = here::here(generated_data_path,name))
  save_image(p, file = path)
  Sys.sleep(5)  # Adjust sleep time as needed
}
```

What do the signals look like? 
Scar versus No Scar

```{r}
# Define a color palette
colors <- brewer.pal(n = 2, name = "Set1") 


p <- cleaned_aggregate_long_data %>% select(Categorical_Label,signal_data,Row,sheep,WaveFront, Catheter_Type, Point_Number) %>% 
  group_by(sheep,WaveFront, Catheter_Type, Point_Number) %>%
  plot_ly(., x = ~Row,y = ~signal_data, type = 'scatter', mode = 'lines',
  color = ~Categorical_Label, colors = colors, line = list(width = 0.5),opacity = 0.8) 
  
save_plot("scar_v_noscar.pdf",p)
#p
```


What do the signals look like? 
WaveFronts
```{r}
colors <- brewer.pal(n = 3, name = "Set3") 

p <- cleaned_aggregate_long_data %>% select(Categorical_Label,signal_data,Row,sheep,WaveFront, Catheter_Type, Point_Number) %>% 
  group_by(sheep,WaveFront, Catheter_Type, Point_Number) %>%
  plot_ly(., x = ~Row,y = ~signal_data, type = 'scatter', mode = 'lines',
  color = ~WaveFront, line = list(width = 0.5),
  colors = colors) 
  
save_plot("scar_by_wavefront.pdf",p)
#p
```

What do the signals look like? 
Sheep

```{r}


colors <- brewer.pal(n = 4, name = "Set3") 

p <- cleaned_aggregate_long_data %>% select(Categorical_Label,signal_data,Row,sheep,WaveFront, Catheter_Type, Point_Number) %>% 
  group_by(sheep,WaveFront, Catheter_Type, Point_Number) %>%
  plot_ly(., x = ~Row,y = ~signal_data, type = 'scatter', mode = 'lines',
  color = ~sheep, line = list(width = 0.5),
  colors = colors) 
  
#p
```

Investigation of particular sheep and wavefront.

```{r}

get_individual_plot <- function(plot_name,select_sheep,select_wavefront ) {
  colors <- brewer.pal(n = 4, name = "Set1") 
  p <- cleaned_aggregate_long_data %>% select(Categorical_Label,signal_data,Row,sheep,WaveFront, Catheter_Type, Point_Number) %>% 
  filter(sheep == select_sheep,WaveFront == select_wavefront) %>% 
  group_by(sheep,WaveFront, Catheter_Type, Point_Number) %>%
  plot_ly(., x = ~Row,y = ~signal_data, type = 'scatter', mode = 'lines',
  color = ~Categorical_Label, line = list(width = 0.4),
  colors = colors)  %>% 
  layout( 
         xaxis = list(title = "Row"),
         yaxis = list(title = "signal"),
         title = paste0(select_sheep," ",select_wavefront," signals"))
  
  save_plot(plot_name,p)
  
  return(p)
  
}

#"S9" "S17" "S18" "S12" "S20" "S15"
#"SR" ("Ap" for S9) "LVp" "RVp" 
#look at individual case
select_sheep <- "S20"
select_wavefront <- "RVp"
p <- get_individual_plot(paste0(select_sheep,"_",select_wavefront,".pdf"),select_sheep,select_wavefront )

#p
```

# run all
```{r}
all_wavefronts <- c("SR","LvP","RvP")
all_sheep <- c("S9","S17","S18","S12","S20","S15")
#saves them all as pdf
for (s in all_sheep) {
  for (w in all_wavefronts){
    p <- get_individual_plot(paste0(s,"_",w,".pdf"),s,w )
    
  }
}
```
